---
title: "Shiny Apps"
output:
  html_document:
    number_sections: false
    toc: yes
params:
  due: "13 April, 11:59 pm"
  purpose: "The purpose of this assignment is to get a quick preview of shiny apps so that you'll be more familiar with the overall structure of shiny apps prior to class."
---

```{r child = "knitr_setup.Rmd"}
```

```{r child = "_rheader.Rmd"}
```

### For this week's reflection, download and edit [this template](https://eda.seas.gwu.edu/2021-Spring/templates/reflection13.zip).

# Watch 

First, watch this 2-minute intro video to get a quick sense for what Shiny apps are: 

<iframe width="560" height="315" src="https://www.youtube.com/embed/HVa42mJYppE?start=25" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>

# View 

Go to the [RStudio Shiny Gallery](https://shiny.rstudio.com/gallery/) and explore some of the Shiny apps to get a sense for what is possible with Shiny.

# Build 

Read through [this tutorial](https://towardsdatascience.com/beginners-guide-to-creating-an-r-shiny-app-1664387d95b3) and use [this template](https://github.com/emse-eda-gwu/2021-Spring/raw/master/templates/shiny_tutorial.zip) to follow along by creating the shiny app on your own computer.

When you're done, you should be able to open the `app.R` file and click the "Run app" button. Your app should look the same as the final version of the app [here](https://yhejazi.shinyapps.io/tutorial/).

# Write 

In your reflection, write about one of the Shiny apps you found most interesting in the RStudio Gallery and any other thoughts you might have about Shiny /  interactivity, or something else that's on your mind or something you've recently experienced related to class.

# Knit and Submit

- Knit your document to a html page.
- Create a zip file of everything in your R Project folder.
- Go to the "Assignment Submission" page on Blackboard and submit your zip file.
