---
title: "Maps"
output:
  html_document:
    number_sections: false
    toc: yes
params:
  due: "30 March, 11:59 pm"
  purpose: 'The purpose of this assignment is to learn some techniques for creating a special type of chart: maps. We will look at different types of maps and how to work with different types of geospatial data.'
---

```{r child = "knitr_setup.Rmd"}
```

```{r child = "_rheader.Rmd"}
```

# Tasks

1. **Read**: Open up a notebook (physical, digital...whatever you take notes in best), and **take notes** while you go through the readings below.

2. **Reflection**: When you have completed all of the readings, download and edit [this template](https://eda.seas.gwu.edu/2021-Spring/templates/reflection11.zip) to write a ~150 word (or more) reflection about on what you've read (be sure to edit the YAML at the top). That's fairly short - there are ~250 words on a typical double-spaced page in Microsoft Word (500 when single-spaced). You can do a lot of different things with this memo, for example:

    - Discuss something you learned from the course content
    - Write about the best or worst data visualization you saw recently
    - Connect the course content to your own work
    - Discuss some of the key insights or things you found interesting in the readings

3. **Submit Everything**: Knit your document to a html page, then create a zip file of everything in your R Project folder. Go to the "Assignment Submission" page on Blackboard and submit your zip file.

---

# Watch 

Watch [this video](https://www.youtube.com/watch?v=kIID5FDi2JQ) on map projections:

<iframe width="560" height="315" src="https://www.youtube.com/embed/kIID5FDi2JQ" frameborder="0" allow="accelerometer; autoplay; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>

# Read 

- Wilke: [15 - Visualizing geospatial data](https://serialmentor.com/dataviz/geospatial-data.html)
- [XKCD: Map projections](https://xkcd.com/977/)
- Healy: [7 - Draw maps](http://socviz.co/maps.html#maps)
- Drawing beautiful maps: Parts [one](https://www.r-spatial.org/r/2018/10/25/ggplot2-sf.html), [two](https://www.r-spatial.org/r/2018/10/25/ggplot2-sf-2.html), & [three](https://www.r-spatial.org/r/2018/10/25/ggplot2-sf-3.html)

# Bonus Points*

Include an image or link to a recent map you've seen (or one you thought was super interesting)

---

*By "bonus points" I mean more like ["brownie points"](https://www.dictionary.com/browse/brownie--points)

