---
title: "Shiny Apps"
output:
  html_document:
    number_sections: false
    toc: yes
params:
  due: "13 April, 11:59 pm"
  purpose: 'The purpose of this assignment is...'
---

```{r child = "knitr_setup.Rmd"}
```

```{r child = "_rheader.Rmd"}
```

# Tasks




This week we will learn about how to make interactive web applications using the [R Shiny package](https://shiny.rstudio.com/). Take a look at some examples of impressive apps built using Shiny:

- [Shiny COVID-19 tracker](https://shiny.rstudio.com/gallery/covid19-tracker.html)
- [A Dashboard for Conference Tweets](https://shiny.rstudio.com/gallery/conference-tweet-dashboard.html)
- [Medcare spending map](https://tychobra.shinyapps.io/medicare-map/)


View more examples at the [RStudio Showcase](https://shiny.rstudio.com/gallery/) and on [Tychobra.com](https://www.tychobra.com/shiny/).

Want to build your own Shiny app? The best place to start an learn more about how to build your own Shiny apps is the [RStudio documentation](https://shiny.rstudio.com/tutorial/).
