---
title: "Correlation"
output:
  html_document:
    number_sections: false
    toc: yes
params:
  due: "02 February, 11:59 pm"
  purpose: 'The purpose of this assignment is to learn some methods to recognize and measure the correlation between two variables as well as how to find a "line of best fit" between them.'
---

```{r child = "knitr_setup.Rmd"}
```

```{r child = "_rheader.Rmd"}
```

# Tasks

1. **Read**: Open up a notebook (physical, digital...whatever you take notes in best), and **take notes** while you go through the readings below.

2. **Optional Exercises**: You don't *have* to do these, but they can be really helpful for extra practice. This week, take a look at the DataCamp course ["Correlation and Regression in R"](https://learn.datacamp.com/courses/correlation-and-regression-in-r).

3. **Reflection**: When you have completed all of the readings, download and edit [this template](https://eda.seas.gwu.edu/2021-Spring/templates/reflection3.zip) to write a  ~150 word reflection about on what you've read (be sure to edit the YAML at the top). That's fairly short - there are ~250 words on a typical double-spaced page in Microsoft Word (500 when single-spaced). You can do a lot of different things with this memo, for example:

    - Discuss something you learned from the course content
    - Write about the best or worst data visualization you saw recently
    - Connect the course content to your own work
    - Discuss some of the key insights or things you found interesting in the readings

5. **Submit Everything**: Knit your document to a html page, then create a zip file of everything in your R Project folder. Go to the "Assignment Submission" page on Blackboard and submit your zip file.

---

# Readings

This week, we will learn some methods to recognize and measure the correlation between two variables as well as how to find a "line of best fit" between them. By the end, you will be able to:

- Recognize when to use correlation.
- Interpret the magnitude and direction of a correlation.
- Explain the influence of outliers.
- Describe the Pearson correlation and the Spearman correlation.
- Explain the term "line of best fit".
- Interpret intercept and slope coefficients.
- Define residuals.
- Describe the standard error of the estimate.
- Report the assumptions of linear regression and how to test them.
- Explain standardized regression and its connection to correlation.

## 1) Readings on visualizing correlation

- [Wilke - 12: Visualizing associations](https://serialmentor.com/dataviz/visualizing-associations.html): An overview of ways to visualize associations between two or more variables.
- ["Beware Spurious Correlations", Harvard Business Review](https://hbr.org/2015/06/beware-spurious-correlations)

**Optional Readings**

Correlation, as innocent as it may seem, has a long and ugly history of racism that should never be forgotten. These readings discuss this topics in more detail:

- [Francis Galton pioneered scientific advances in many fields – but also founded the racist pseudoscience of eugenics](https://theconversation.com/francis-galton-pioneered-scientific-advances-in-many-fields-but-also-founded-the-racist-pseudoscience-of-eugenics-144465)
- [Column: The false, racist theory of eugenics once ruled science. Let’s never let that happen again](https://www.pbs.org/newshour/nation/column-the-false-racist-theory-of-eugenics-once-ruled-science-lets-never-let-that-happen-again)
- Listen to [this Radiolab episode](https://podcasts.apple.com/us/podcast/g-unfit/id152249110?i=1000444689017) on eugenics.

## 2) Videos on correlation and regression

<iframe width="560" height="315" src="https://www.youtube.com/embed/fmK5YWWobH8" frameborder="0" allow="accelerometer; autoplay; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>

<iframe width="560" height="315" src="https://www.youtube.com/embed/kXDRkUqzD6g" frameborder="0" allow="accelerometer; autoplay; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>
