---
title: "Visualizing Information"
output:
  html_document:
    number_sections: false
    toc: yes
params:
  due: "09 February, 11:59 pm"
  purpose: 'The purpose of this assignment is to learn what makes a "good" information visualization, which is _not_ entirely a subjective judgment. There are a wide variety of design principles available to help guide the creation of clear, effective information visualizations, many of which are rooted in research on human psychology.'
---

```{r child = "knitr_setup.Rmd"}
```

```{r child = "_rheader.Rmd"}
```

# Tasks

1. **Read**: Open up a notebook (physical, digital...whatever you take notes in best), and **take notes** while you go through the readings below.

2. **Reflection**: When you have completed all of the readings, download and edit [this template](https://eda.seas.gwu.edu/2021-Spring/templates/reflection4.zip) to write a  ~150 word reflection about on what you've read (be sure to edit the YAML at the top). That's fairly short - there are ~250 words on a typical double-spaced page in Microsoft Word (500 when single-spaced). You can do a lot of different things with this memo, for example:

    - Discuss something you learned from the course content
    - Write about the best or worst data visualization you saw recently
    - Connect the course content to your own work
    - Discuss some of the key insights or things you found interesting in the readings

3. **Submit Everything**: Knit your document to a html page, then create a zip file of everything in your R Project folder. Go to the "Assignment Submission" page on Blackboard and submit your zip file.

---

# Readings

> "Data visualization is part art and part science. The challenge is to get the art right without getting the science wrong and vice versa."
>
> -- Claus O. Wilke in [Fundamentals of Data Visualization](https://serialmentor.com/dataviz/introduction.html)

These two chapters cover a lot of excellent examples of what makes a chart "good" and "bad":

- [Healy 1: Look at Data](http://socviz.co/lookatdata.html#lookatdata): What makes figures good and bad
- [Wilke 1: Introduction](https://serialmentor.com/dataviz/introduction.html): Definitions of "ugly", "bad", and "wrong" figures

# Optional Video

If you have time, watch [this 40-minute video](https://www.youtube.com/watch?v=fSgEeI2Xpdc) titled "How humans see data", by John Rauser. He discusses how we can exploit our understanding of human psychology to design effective charts (I'll cover much of the same information in the video in class).

<center>
<iframe width="560" height="315" src="https://www.youtube.com/embed/fSgEeI2Xpdc" frameborder="0" allow="accelerometer; autoplay; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>
</center>
