---
title: "Comparisons"
output:
  html_document:
    number_sections: false
    toc: yes
params:
  due: "23 February, 11:59 pm"
  purpose: 'The purpose of this assignment is to learn some of the technical details of how to create charts for **comparing values** to one another and / or to a benchmark.'
---

```{r child = "knitr_setup.Rmd"}
```

```{r child = "_rheader.Rmd"}
```

# Tasks

1. **Read**: Open up a notebook (physical, digital...whatever you take notes in best), and **take notes** while you go through the readings below.

2. **Reflection**: When you have completed all of the readings, download and edit [this template](https://eda.seas.gwu.edu/2021-Spring/templates/reflection6.zip) to write a ~150 word (or more) reflection about on what you've read (be sure to edit the YAML at the top). That's fairly short - there are ~250 words on a typical double-spaced page in Microsoft Word (500 when single-spaced). You can do a lot of different things with this memo, for example:

    - Discuss something you learned from the course content
    - Write about the best or worst data visualization you saw recently
    - Connect the course content to your own work
    - Discuss some of the key insights or things you found interesting in the readings

3. **Make a Chart**: Once you've read through everything, add a code chunk in your reflection that creates one of the charts you saw in one of the readings. **Cite the source** of the chart. The goal is to try and reproduce the chart as closely as possible to how it looks in the reading, so it is perfectly fine to copy-paste code directly into your reflection. You may need to modify the figure dimensions in the chunk settings.

4. **Submit Everything**: Knit your document to a html page, then create a zip file of everything in your R Project folder. Go to the "Assignment Submission" page on Blackboard and submit your zip file.

---

# Readings

> "At the heart of quantitative reasoning is a single question: Compared to what?"
>
> -- Edward Tufte

Most of the readings this week have code in them that illustrate how to create each chart type, and I encourage you to try and reproduce the examples provided in R yourself. You may also want to take a look at the [top 50 ggplots](http://r-statistics.co/Top50-Ggplot2-Visualizations-MasterList-R-Code.html), which contains examples with ggplot code to create 50 common visualizations.

Plot types for comparing values:

- [Slopes](http://r-statistics.co/Top50-Ggplot2-Visualizations-MasterList-R-Code.html#Slope%20Chart)
- [Bullets](http://www.storytellingwithdata.com/blog/2017/5/25/the-bullet-graph)
- [Dumbell plots](http://uc-r.github.io/cleveland-dot-plots)
- Wilke: [7 - Visualizing distributions](https://serialmentor.com/dataviz/histograms-density-plots.html)
- Wilke: [9 - Visualizing many distributions at once](https://serialmentor.com/dataviz/boxplots-violins.html)

Optional reading:

- [Dual-Scaled Axes in Graphs - Are They Ever the Best Solution?](http://www.perceptualedge.com/articles/visual_business_intelligence/dual-scaled_axes.pdf)
