---
title: "Trends"
output:
  html_document:
    number_sections: false
    toc: yes
params:
  due: "02 March, 11:59 pm"
  purpose: 'The purpose of this assignment is to learn some of the technical details of how to create charts that highlight **trends**, which inherently involve changes in values over time.'
---

```{r child = "knitr_setup.Rmd"}
```

```{r child = "_rheader.Rmd"}
```

# Tasks

1. **Read**: Open up a notebook (physical, digital...whatever you take notes in best), and **take notes** while you go through the readings below.

2. **Reflection**: When you have completed all of the readings, download and edit [this template](https://eda.seas.gwu.edu/2021-Spring/templates/reflection7.zip) to write a ~150 word (or more) reflection about on what you've read (be sure to edit the YAML at the top). That's fairly short - there are ~250 words on a typical double-spaced page in Microsoft Word (500 when single-spaced). You can do a lot of different things with this memo, for example:

    - Discuss something you learned from the course content
    - Write about the best or worst data visualization you saw recently
    - Connect the course content to your own work
    - Discuss some of the key insights or things you found interesting in the readings

3. **Submit Everything**: Knit your document to a html page, then create a zip file of everything in your R Project folder. Go to the "Assignment Submission" page on Blackboard and submit your zip file.

---

# Readings

Most of the readings this week have code in them that illustrate how to create each chart type, and I encourage you to try and reproduce the examples provided in R yourself.

- Wilke: [13 - Visualizing time series](https://serialmentor.com/dataviz/time-series.html)
- Wilke: [14 - Visualizing trends](https://serialmentor.com/dataviz/visualizing-trends.html)

Some examples of visualizations we'll explore in class:

- The "bar chart race": [Changes in how couples meet over time](https://flowingdata.com/2019/03/15/shifts-in-how-couples-meet-online-takes-the-top-spot/)
- The heatmap: [How common is your birthday?](http://thedailyviz.com/2016/09/17/how-common-is-your-birthday-dailyviz/)
- [Time-Series Heatmaps](https://towardsdatascience.com/time-series-calendar-heatmaps-9f576578fcfe)

Optional:

- [The Sankey diagrams (a.k.a. flow chart)](https://www.data-to-viz.com/graph/sankey.html)
- Video: [The fallen of WWII](http://www.fallen.io/ww2/)

# Video 

This video by Hans Rosling is a great summary of his larger [TED talk](https://www.ted.com/talks/hans_rosling_the_best_stats_you_ve_ever_seen) on the "gapminder" project he started showing life expectancy and GDP over time. This is an excellent example of using an _animated_ chart to tell a much richer story than a static chart.

<iframe width="560" height="315" src="https://www.youtube.com/embed/jbkSRLYSojo" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>
