---
title: "Cleaning Data"
output:
  html_document:
    number_sections: false
    toc: yes
params:
  due: "09 March, 11:59 pm"
  purpose: 'The purpose of this assignment is learn some techniques for dealing with messy data. Most of the time, the raw data you get is in the wrong format and variables are not properly coded, so you will need to "clean" the data before starting any analysis. Other times the data will be split into two or more data sets, and you will need to "join" them together into a single data frame.'
---

```{r child = "knitr_setup.Rmd"}
```

```{r child = "_rheader.Rmd"}
```

# Tasks

1. **Read**: Open up a notebook (physical, digital...whatever you take notes in best), and **take notes** while you go through the readings below.

2. **Reflection**: When you have completed all of the readings, download and edit [this template](https://eda.seas.gwu.edu/2021-Spring/templates/reflection8.zip) to write a ~150 word (or more) reflection about on what you've read (be sure to edit the YAML at the top). That's fairly short - there are ~250 words on a typical double-spaced page in Microsoft Word (500 when single-spaced). You can do a lot of different things with this memo, for example:

    - Discuss something you learned from the course content
    - Write about the best or worst data visualization you saw recently
    - Connect the course content to your own work
    - Discuss some of the key insights or things you found interesting in the readings

3. **Submit Everything**: Knit your document to a html page, then create a zip file of everything in your R Project folder. Go to the "Assignment Submission" page on Blackboard and submit your zip file.

---

# Readings

- [Stat 545 chapter 15 on joining two tables](https://stat545.com/join-cheatsheet.html)
- [Tips for Cleaning Messy Data in R](https://rfortherestofus.com/2019/12/how-to-clean-messy-data-in-r/)
- [This case study](https://www.rpubs.com/justinhtet/cleaning-messy-weather-dataset-with-tidyverse) of cleaning up some terribly messy weather data.

# Optional Practice

If you want some extra practice working with data in R, check out Alison Hill's course on DataCamp: [Working with Data in the Tidyverse](https://learn.datacamp.com/courses/working-with-data-in-the-tidyverse). In particular, I suggest going through parts 2 ("Tame your data") and 4 ("Transform your data")

# Bonus Points*

In your reflection this week, share a story about or link to the messiest data you've ever come across.

---

*There are no actual bonus points
