---
title: "Getting Started"
subtitle: "EMSE 4575: Exploratory Data Analysis"
date: January 12, 2021
week: 1
output: html_document
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(readxl)
knitr::opts_chunk$set(
    warning = FALSE,
    message = FALSE,
    fig.path = "figs/",
    fig.width = 7.252,
    fig.height = 4,
    comment = "#>",
    fig.retina = 3
)
```

# Practice 1 - Importing Data

Write code to import the following data files from the "data" folder:

- `lotr_words.csv`
- `north_america_bear_killings.txt`
- `uspto_clean_energy_patents.xlsx`

```{r, include=FALSE}
lotr_words <- read_csv(here('data', 'lotr_words.csv'))

bear_killings <- read.table(here('data', 'north_america_bear_killings.txt'),
                            header = TRUE)

patents <- read_excel(here('data', 'uspto_clean_energy_patents.xlsx'),
                       sheet = 'Figure 6-45', skip = 3)
```



# Practice 2 - Data Provenance

Documentation in the "data/README.md" file is missing for the following data sets:

1. wildlife_impacts.csv (Breakout Rooms 1 & 2):
https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-07-23

2. north_america_bear_killings.txt (Breakout Rooms 3 & 4):
https://data.world/makeovermonday/2019w21

3. uspto_clean_energy_patents.xlsx (Breakout Rooms 5 & 6):
https://www.nsf.gov/statistics/2018/nsb20181/report/sections/industry-technology-and-the-global-marketplace/global-trends-in-sustainable-energy-research-and-technologies

Go to the above sites and add the following information to the "data/README.md" file:

- The name of the downloaded file.
- The web address to the site you downloaded the data from.
- The source of the _original_ data (if different from the website).
- A short description of the data and how they were collected.
- A dictionary for the data (hint: the site might already have this!).

### wildlife_impacts.csv

Data file: `wildlife_impacts.csv`

Date downloaded: January 5, 2020

Description: Impacts of wildlife with aircraft by 4 major US airlines - 70% of the full database. Also, the data have been pre-processed.

Source of downloaded file:
- The Tidy Tuesday challenge here: https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-07-23
- Here's the link to the original file I downloaded: https://github.com/rfordatascience/tidytuesday/blob/master/data/2019/2019-07-23/wildlife_impacts.csv?raw=true

Original data source:
- FAA wildlife strike database: https://wildlife.faa.gov/home

Notes:
- Note that the wildlife impact data is only from the big 4 airlines - 70% of the full database.
- The data have been pre-processed

Link to full data dictionary:
https://wildlife.faa.gov/downloads/fieldlist.xls

### north_america_bear_killings.txt

Data file: `north_america_bear_killings.txt`

Date downloaded: January 15, 2020

Description: Bear killings in the U.S.

Source of downloaded file: https://data.world/makeovermonday/2019w21

Original source: The data was found on Wikipedia and collected, prepared, and distributed by Ali Sanne on data.world.

variable        | description
----------------|----------------------
Name            | Name of victim
age             | Age of victim
gender          | Gender of victim
Date            | Date of incident
Month           | Month of incident
Year            | Year of incident
Type            | type
Location        | Location of incident
Description     | Description of incident
Type of bear    | Type of bear
Hunter          | Whether the victim was a hunter
Grizzly         | Whether the bear was a brizzly
Hikers          | Whether the victim was a hiker
Only one killed | Whether there was only one victim killed

### uspto_clean_energy_patents.xlsx

Data file: `uspto_clean_energy_patents.xlsx`

Date downloaded: January 24, 2020

Description: USPTO patents in clean energy technologies.

Original source:
Science-Metrix, PatentsView, and USPTO patent data. See Appendix Table 6-57.
Science and Engineering Indicators 2018
https://www.nsf.gov/statistics/2018/nsb20181/assets/1235/tables/at06-56.xlsx

Details (from source): Sustainable energy technologies include alternative energy, energy storage, smart grid, and pollution mitigation. Alternative energy includes solar; wind; nuclear; fuel cell; hydropower; wave, tidal, ocean; geothermal; and electric or hybrid. Energy storage includes batteries, compressed air, flywheels, superconductivity, magnet energy systems, ultracapacitors, hydrogen production and storage, and thermal energy. Pollution mitigation includes recycling; control of air, water, and solid waste pollution; environmental remediation; cleaner coal; and capture and storage of carbon and other greenhouse gases. Technologies are classified by The Patent Board. Patent grants are fractionally allocated among regions or countries on the basis of the proportion of the residences of all named inventors.

Link to full report here: https://www.nsf.gov/statistics/2018/nsb20181/report/sections/industry-technology-and-the-global-marketplace/global-trends-in-sustainable-energy-research-and-technologies







# Practice 3 - Tidy Data

1. Use `spread()` to "untidy" the `milk_production` data into a format where the columns are state names and the values are the milk produced in each state.

2. Use `gather()` to "tidy" the `pv_cells` data into a data frame with three names: `year`, `country`, `numCells`

```{r}
milk_wide <- milk_production %>%
    spread(key = state, value = milk_produced)

pv_cells_long <- pv_cells %>%
    gather(key = "country", value = "numCells", China:World)
```
