---
title: "Getting Started"
subtitle: "EMSE 4575: Exploratory Data Analysis"
date: January 12, 2021
week: 1
output: html_document
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(readxl)
knitr::opts_chunk$set(
    warning = FALSE,
    message = FALSE,
    fig.path = "figs/",
    fig.width = 7.252,
    fig.height = 4,
    comment = "#>",
    fig.retina = 3
)
```

# Practice 1 - Importing Data

Write code to import the following data files from the "data" folder:

- `lotr_words.csv`
- `north_america_bear_killings.txt`
- `uspto_clean_energy_patents.xlsx`

```{r}

```



# Practice 2 - Data Provenance

Documentation in the "data/README.md" file is missing for the following data sets:

1. wildlife_impacts.csv (Breakout Rooms 1 & 2):
https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-07-23

2. north_america_bear_killings.txt (Breakout Rooms 3 & 4):
https://data.world/makeovermonday/2019w21

3. uspto_clean_energy_patents.xlsx (Breakout Rooms 5 & 6):
https://www.nsf.gov/statistics/2018/nsb20181/report/sections/industry-technology-and-the-global-marketplace/global-trends-in-sustainable-energy-research-and-technologies

Go to the above sites and add the following information to the "data/README.md" file:

- The name of the downloaded file.
- The web address to the site you downloaded the data from.
- The source of the _original_ data (if different from the website).
- A short description of the data and how they were collected.
- A dictionary for the data (hint: the site might already have this!).






# Practice 3 - Tidy Data

1. Use `spread()` to "untidy" the `milk_production` data into a format where the columns are state names and the values are the milk produced in each state.

2. Use `gather()` to "tidy" the `pv_cells` data into a data frame with three names: `year`, `country`, `numCells`

```{r}

```
